Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2018-02-02 manuscript/tracer17.tex
Added paragraph about other packages. Probably needs work.

>>>>

Other packages are available for the post-processing of MCMC samples are available and are largely complementary to \tracer\. The R package `coda' \citep{plummer2006coda} provides some of the functionality of \tracer\ within the R programming environment. `AWTY' \citep{nylander2007awty} looks at the convergence of phylogenetic MCMC runs for the phylogenetic tree itself. %% AR - anything else? The MDS tree-space approaches of Hillis etc.?
